%
% Journal title abbreviations for institutional and geographic terms.
%
%\hi@abbrev{Houston}{Hous.}
%\hi@abbrev{Rutgers-Camden}{Rutgers-Cam.}
\hi@abbrev{Adelaide}{Adel.}
\hi@abbrev{Air Force}{A.F.}
\hi@abbrev{Albany}{Alb.}
\hi@abbrev{American Bar Association}{A.B.A.}
\hi@abbrev{American Intellectual Property Law Association}{AIPLA}
\hi@abbrev{American Law Institute}{A.L.I.}
\hi@abbrev{American Medical Association}{AMA}
\hi@abbrev{American Society of Composers Authors and Publishers}{ASCAP}
\hi@abbrev{American Society of Composers, Authors and Publishers}{ASCAP}
\hi@abbrev{Boston College}{B.C.}
\hi@abbrev{Boston University}{B.U.}
\hi@abbrev{Brigham Young University}{BYU}
\hi@abbrev{Brooklyn}{Brook.}
\hi@abbrev{Buffalo}{Buff.}
\hi@abbrev{Chapman}{Chap.}
\hi@abbrev{Chartered Life Underwriters}{C.L.U.}
\hi@abbrev{Cincinnati}{Cin.}
\hi@abbrev{City University of New York}{CUNY}
\hi@abbrev{Cleveland}{Clev.}
\hi@abbrev{College}{C.}
\hi@abbrev{Columbia}{Colum.}
\hi@abbrev{Cumberland}{Cumb.}
\hi@abbrev{Denver}{Denv.}
\hi@abbrev{Detroit}{Det.}
\hi@abbrev{Dickinson}{Dick.}
\hi@abbrev{Duquesne}{Duq.}
\hi@abbrev{Federal Circuit}{Fed. Cir.}
\hi@abbrev{Florida International University}{FIU}
\hi@abbrev{Foreign Broadcast Information Service}{F.B.I.S.}
\hi@abbrev{George Mason}{Geo. Mason}
\hi@abbrev{George Washington}{Geo. Wash.}
\hi@abbrev{Georgetown}{Geo.}
\hi@abbrev{George}{Geo.}
\hi@abbrev{Gonzaga}{Gonz.}
\hi@abbrev{Harvard}{Harv.}
\hi@abbrev{Howard}{How.}
\hi@abbrev{Institute}{Inst.}
\hi@abbrev{John Marshall}{J. Marshall}
\hi@abbrev{Journal of the American Medical Association}{JAMA}
\hi@abbrev{Judge Advocate General's}{JAG}
\hi@abbrev{Judge Advocate General}{JAG}
\hi@abbrev{Las Vegas}{L.V.}
\hi@abbrev{Law School}{L. Sch.} % To ensure the "Law" is part of institution
\hi@abbrev{Lawyers Reports Annotated}{L.R.A.}
\hi@abbrev{Loyola}{Loy.}
\hi@abbrev{Marquette}{Marq.}
\hi@abbrev{Melbourne}{Melb.}
\hi@abbrev{Memphis}{Mem.}
\hi@abbrev{Pepperdine}{Pepp.}
\hi@abbrev{Pittsburgh}{Pitt.}
\hi@abbrev{Puertorriqueno}{P.R.}
\hi@abbrev{Richmond}{Rich.}
\hi@abbrev{Rocky Mountain}{Rocky Mtn.}
\hi@abbrev{Saint Louis}{St. Louis}
\hi@abbrev{Saint}{St.}
\hi@abbrev{San Fernando Valley}{San Fern. V.}
\hi@abbrev{Southern Methodist University}{SMU}
\hi@abbrev{Stanford}{Stan.}
\hi@abbrev{State}{St.}
\hi@abbrev{Temple}{Temp.}
\hi@abbrev{Thomas Jefferson}{T. Jefferson}
\hi@abbrev{Thomas M. Cooley}{T.M. Cooley}
\hi@abbrev{Thurgood Marshall}{T. Marshall}
\hi@abbrev{Toledo}{Tol.}
\hi@abbrev{Tulane}{Tul.}
\hi@abbrev{Universidad de Puerto Rico}{U.~P.R.}
\hi@abbrev{Universidad}{U.}
\hi@abbrev{Universities}{U.}
\hi@abbrev{University of California Los Angeles}{UCLA}
\hi@abbrev{University of California}{U.C.}
\hi@abbrev{University of Missouri Kansas City}{UKMC}
\hi@abbrev{University of West Los Angeles}{UWLA}
\hi@abbrev{University of the District of Columbia David Clarke School of Law}{UDC/DCSL}
\hi@abbrev{Valparaiso}{Val.}
\hi@abbrev{Vanderbilt}{Vand.}
\hi@abbrev{Villanova}{Vill.}
\hi@abbrev{William Mitchell}{Wm. Mitchell}
\hi@abbrev{William and Mary}{Wm. \& Mary}
\hi@abbrev{William}{Wm.}
