%
% Abbreviations for journal words, from Indigo Book Table 18
%
\hi@abbrev{Academic}{Acad.}
\hi@abbrev{Academics}{Acads.}
\hi@abbrev{Academy}{Acad.}
\hi@abbrev{Academies}{Acads.}
\hi@abbrev{Accountant}{Acct.}
\hi@abbrev{Accountants}{Acct.}
\hi@abbrev{Accounting}{Acct.}
\hi@abbrev{Accountings}{Accts.}
\hi@abbrev{Accountancy}{Acct.}
\hi@abbrev{Accountancies}{Accts.}
\hi@abbrev{Administrative}{Admin.}
\hi@abbrev{Administratives}{Admins.}
\hi@abbrev{Administrator}{Admin.}
\hi@abbrev{Administrators}{Admins.}
\hi@abbrev{Administration}{Admin.}
\hi@abbrev{Administrations}{Admins.}
\hi@abbrev{Advertising}{Advert.}
\hi@abbrev{Advertisings}{Adverts.}
\hi@abbrev{Advocate}{Advoc.}
\hi@abbrev{Advocates}{Advocs.}
\hi@abbrev{Advocacy}{Advoc.}
\hi@abbrev{Advocacies}{Advocs.}
\hi@abbrev{Affairs}{Aff.}
\hi@abbrev{Affairses}{Affs.}
\hi@abbrev{African}{Afr.}
\hi@abbrev{Africans}{Afrs.}
\hi@abbrev{Agriculture}{Agric.}
\hi@abbrev{Agricultures}{Agrics.}
\hi@abbrev{Agricultural}{Agric.}
\hi@abbrev{Agriculturals}{Agrics.}
\hi@abbrev{Amendment}{Amend.}
\hi@abbrev{Amendments}{Amends.}
\hi@abbrev{American}{Am.}
\hi@abbrev{Americans}{Ams.}
\hi@abbrev{Americas}{Am.}
\hi@abbrev{Americases}{Ams.}
\hi@abbrev{Ancestry}{Anc.}
\hi@abbrev{Ancestries}{Ancs.}
\hi@abbrev{and}{\&}
\hi@abbrev{ands}{\&s}
\hi@abbrev{Annual}{Ann.}
\hi@abbrev{Annuals}{Anns.}
\hi@abbrev{Appellate}{App.}
\hi@abbrev{Appellates}{Apps.}
\hi@abbrev{Arbitration}{Arb.}
\hi@abbrev{Arbitrations}{Arbs.}
\hi@abbrev{Arbitrator}{Arb.}
\hi@abbrev{Arbitrators}{Arb.}
\hi@abbrev{Association}{Ass'n}
\hi@abbrev{Associations}{Ass'ns}
\hi@abbrev{Attorney}{Att'y}
\hi@abbrev{Attorneys}{Att'ys}
\hi@abbrev{Bankruptcy}{Bankr.}
\hi@abbrev{Bankruptcies}{Bankrs.}
\hi@abbrev{Bar}{B\abb@dot }
\hi@abbrev{Bars}{Bs.}
\hi@abbrev{Behavioral}{Behav.}
\hi@abbrev{Behaviorals}{Behavs.}
\hi@abbrev{British}{Brit.}
\hi@abbrev{Britishes}{Brits.}
\hi@abbrev{Bulletin}{Bull.}
\hi@abbrev{Bulletins}{Bulls.}
\hi@abbrev{Business}{Bus.}
\hi@abbrev{Businesses}{Buss.}
\hi@abbrev{Capitals}{Caps.}
\hi@abbrev{Catholic}{Cath.}
\hi@abbrev{Catholics}{Caths.}
\hi@abbrev{Center}{Ctr.}
\hi@abbrev{Centers}{Ctrs.}
\hi@abbrev{Centre}{Ctr.}
\hi@abbrev{Centres}{Ctrs.}
\hi@abbrev{Central}{Cent.}
\hi@abbrev{Centrals}{Cents.}
\hi@abbrev{Children's}{Child.}
\hi@abbrev{Chronicle}{Chron.}
\hi@abbrev{Chronicles}{Chrons.}
\hi@abbrev{Circuit}{Cir.}
\hi@abbrev{Circuits}{Cirs.}
\hi@abbrev{Civil}{Civ.}
\hi@abbrev{Civils}{Civs.}
\hi@abbrev{Civil Liberty}{C\abb@dot L\abb@dot }
\hi@abbrev{Civil Liberties}{C\abb@dot L\abb@dot }
\hi@abbrev{Civil Rights}{C\abb@dot R\abb@dot }
\hi@abbrev{Civil Rightses}{C\abb@dot Rs.}
\hi@abbrev{Commentary}{Comment.}
\hi@abbrev{Commentaries}{Comments.}
\hi@abbrev{Commerce}{Com.}
\hi@abbrev{Commerces}{Coms.}
\hi@abbrev{Commercial}{Com.}
\hi@abbrev{Commercials}{Coms.}
\hi@abbrev{Communications}{Comm.}
\hi@abbrev{Communicationses}{Comms.}
\hi@abbrev{Comparative}{Comp.}
\hi@abbrev{Comparatives}{Comps.}
\hi@abbrev{Conference}{Conf.}
\hi@abbrev{Conferences}{Confs.}
\hi@abbrev{Congressional}{Cong.}
\hi@abbrev{Congressionals}{Congs.}
\hi@abbrev{Constitutional}{Const.}
\hi@abbrev{Constitutionals}{Consts.}
\hi@abbrev{Contemporary}{Contemp.}
\hi@abbrev{Contemporaries}{Contemps.}
\hi@abbrev{Contracts}{Cont.}
\hi@abbrev{Contractses}{Conts.}
\hi@abbrev{Conveyancer}{Conv.}
\hi@abbrev{Conveyancers}{Convs.}
\hi@abbrev{Corporate}{Corp.}
\hi@abbrev{Corporates}{Corps.}
\hi@abbrev{Corporation}{Corp.}
\hi@abbrev{Corporations}{Corps.}
\hi@abbrev{Cosmetic}{Cosm.}
\hi@abbrev{Cosmetics}{Cosms.}
\hi@abbrev{Counselor}{Couns.}
\hi@abbrev{Counselors}{Couns.}
\hi@abbrev{Counselor's}{Couns.}
\hi@abbrev{Court}{Ct.}
\hi@abbrev{Courts}{Cts.}
\hi@abbrev{Courts}{Cts.}
\hi@abbrev{Courtses}{Ctss.}
\hi@abbrev{Criminal}{Crim.}
\hi@abbrev{Criminals}{Crims.}
\hi@abbrev{Defense}{Def.}
\hi@abbrev{Defenses}{Defs.}
\hi@abbrev{Delinquency}{Delinq.}
\hi@abbrev{Delinquencies}{Delinqs.}
\hi@abbrev{Department}{Dep't}
\hi@abbrev{Departments}{Dep'ts}
\hi@abbrev{Derecho}{Der.}
\hi@abbrev{Derechos}{Ders.}
\hi@abbrev{Developments}{Dev.}
\hi@abbrev{Developmentses}{Devs.}
\hi@abbrev{Digest}{Dig.}
\hi@abbrev{Digests}{Digs.}
\hi@abbrev{Diplomacy}{Dipl.}
\hi@abbrev{Diplomacies}{Dipls.}
\hi@abbrev{Dispute}{Disp.}
\hi@abbrev{Disputes}{Disps.}
\hi@abbrev{Doctor}{Dr.}
\hi@abbrev{Doctors}{Drs.}
\hi@abbrev{Easterns}{Es.}
\hi@abbrev{Economic}{Econ.}
\hi@abbrev{Economics}{Econ.}
\hi@abbrev{Economical}{Econ.}
\hi@abbrev{Economicals}{Econs.}
\hi@abbrev{Economy}{Econ.}
\hi@abbrev{Economies}{Econs.}
\hi@abbrev{Educational}{Educ.}
\hi@abbrev{Educationals}{Educs.}
\hi@abbrev{Employee}{Emp.}
\hi@abbrev{Employees}{Emps.}
\hi@abbrev{Employment}{Emp.}
\hi@abbrev{Employments}{Emps.}
\hi@abbrev{English}{Eng.}
\hi@abbrev{Englishes}{Engs.}
\hi@abbrev{Entertainment}{Ent.}
\hi@abbrev{Entertainments}{Ents.}
\hi@abbrev{Environment}{Env't}
\hi@abbrev{Environments}{Env'ts}
\hi@abbrev{Environmental}{Envtl.}
\hi@abbrev{Environmentals}{Envtls.}
\hi@abbrev{Estates}{Est.}
\hi@abbrev{European}{Eur.}
\hi@abbrev{Europeans}{Eurs.}
\hi@abbrev{Faculty}{Fac.}
\hi@abbrev{Faculties}{Facs.}
\hi@abbrev{Family}{Fam.}
\hi@abbrev{Families}{Fams.}
\hi@abbrev{Federal}{Fed.}
\hi@abbrev{Federals}{Feds.}
\hi@abbrev{Federation}{Fed'n}
\hi@abbrev{Federations}{Fed'ns}
\hi@abbrev{Finance}{Fin.}
\hi@abbrev{Finances}{Fins.}
\hi@abbrev{Financial}{Fin.}
\hi@abbrev{Financials}{Fins.}
\hi@abbrev{Fortnightly}{Fort.}
\hi@abbrev{Fortnightlies}{Forts.}
\hi@abbrev{Forum}{F\abb@dot }
\hi@abbrev{Fora}{Fs.}
\hi@abbrev{Forums}{Fs.}
\hi@abbrev{Foundations}{Found.}
\hi@abbrev{Foundationses}{Founds.}
\hi@abbrev{General}{Gen.}
\hi@abbrev{Generals}{Gens.}
\hi@abbrev{Government}{Gov't}
\hi@abbrev{Governments}{Gov'ts}
\hi@abbrev{Hispanic}{Hisp.}
\hi@abbrev{Hispanics}{Hisps.}
\hi@abbrev{Historical}{Hist.}
\hi@abbrev{Historicals}{Hists.}
\hi@abbrev{History}{Hist.}
\hi@abbrev{Histories}{Hists.}
\hi@abbrev{Hospital}{Hosp.}
\hi@abbrev{Hospitals}{Hosps.}
\hi@abbrev{Human}{Hum.}
\hi@abbrev{Humans}{Hums.}
\hi@abbrev{Humanity}{Human.}
\hi@abbrev{Humanities}{Human.}
\hi@abbrev{Immigration}{Immigr.}
\hi@abbrev{Immigrations}{Immigrs.}
\hi@abbrev{Independent}{Indep.}
\hi@abbrev{Independents}{Indeps.}
\hi@abbrev{Industrial}{Indus.}
\hi@abbrev{Industrials}{Induss.}
\hi@abbrev{Inequality}{Ineq.}
\hi@abbrev{Inequalities}{Ineqs.}
\hi@abbrev{Information}{Info.}
\hi@abbrev{Informations}{Infos.}
\hi@abbrev{Injury}{Inj.}
\hi@abbrev{Injuries}{Injs.}
\hi@abbrev{Institute}{Inst.}
\hi@abbrev{Institutes}{Insts.}
\hi@abbrev{Insurance}{Ins.}
\hi@abbrev{Insurances}{Inss.}
\hi@abbrev{Intellectual}{Intell.}
\hi@abbrev{Intellectuals}{Intells.}
\hi@abbrev{Interdisciplinary}{Interdisc.}
\hi@abbrev{Interdisciplinaries}{Interdiscs.}
\hi@abbrev{Interest}{Int.}
\hi@abbrev{Interests}{Ints.}
\hi@abbrev{International}{Int'l}
\hi@abbrev{Internationals}{Int'ls}
\hi@abbrev{Investments}{Inv.}
\hi@abbrev{Investmentses}{Invs.}
\hi@abbrev{Investors}{Inv.}
\hi@abbrev{Investorses}{Invs.}
\hi@abbrev{Journal}{J\abb@dot }
\hi@abbrev{Journals}{Js.}
\hi@abbrev{Judicial}{Jud.}
\hi@abbrev{Judicials}{Juds.}
\hi@abbrev{Juridical}{Jurid.}
\hi@abbrev{Juridicals}{Jurids.}
\hi@abbrev{Jurisprudence}{Juris.}
\hi@abbrev{Jurisprudences}{Juriss.}
\hi@abbrev{Justice}{Just.}
\hi@abbrev{Justices}{Justs.}
\hi@abbrev{Juvenile}{Juv.}
\hi@abbrev{Juveniles}{Juvs.}
\hi@abbrev{Labor}{Lab.}
\hi@abbrev{Labors}{Labs.}
\hi@abbrev{Law}{L\abb@dot }
\hi@abbrev{Laws}{Ls.}
\hi@abbrev{{}Law}{Law}
\hi@abbrev{{}Laws}{Laws}
\hi@abbrev{Lawyers}{Law.}
\hi@abbrev{Lawyerses}{Laws.}
\hi@abbrev{Lawyers'}{Law.}
\hi@abbrev{Lawyer's}{Law.}
\hi@abbrev{Legislation}{Legis.}
\hi@abbrev{Legislations}{Legiss.}
\hi@abbrev{Legislative}{Legis.}
\hi@abbrev{Legislatives}{Legiss.}
\hi@abbrev{Library}{Libr.}
\hi@abbrev{Librarian}{Libr.}
\hi@abbrev{Librarians}{Librs.}
\hi@abbrev{Libraries}{Libr.}
\hi@abbrev{Litigation}{Litig.}
\hi@abbrev{Litigations}{Litigs.}
\hi@abbrev{Local}{Loc.}
\hi@abbrev{Locals}{Locs.}
\hi@abbrev{Magazine}{Mag.}
\hi@abbrev{Magazines}{Mags.}
\hi@abbrev{Management}{Mgmt.}
\hi@abbrev{Managements}{Mgmts.}
\hi@abbrev{Maritime}{Mar.}
\hi@abbrev{Maritimes}{Mars.}
\hi@abbrev{Market}{Mkt.}
\hi@abbrev{Markets}{Mkts.}
\hi@abbrev{Matrimonial}{Matrim.}
\hi@abbrev{Matrimonials}{Matrims.}
\hi@abbrev{Medical}{Med.}
\hi@abbrev{Medicals}{Meds.}
\hi@abbrev{Medicine}{Med.}
\hi@abbrev{Medicines}{Meds.}
\hi@abbrev{Military}{Mil.}
\hi@abbrev{Militaries}{Mils.}
\hi@abbrev{Mineral}{Min.}
\hi@abbrev{Minerals}{Mins.}
\hi@abbrev{Modern}{Mod.}
\hi@abbrev{Moderns}{Mods.}
\hi@abbrev{Municipal}{Mun.}
\hi@abbrev{Municipals}{Muns.}
\hi@abbrev{National}{Nat'l}
\hi@abbrev{Nationals}{Nat'ls}
\hi@abbrev{Nationality}{Nat'lity}
\hi@abbrev{Nationalities}{Nat'litys}
\hi@abbrev{Natural}{Nat.}
\hi@abbrev{Naturals}{Nats.}
\hi@abbrev{Negligence}{Negl.}
\hi@abbrev{Negligences}{Negls.}
\hi@abbrev{Negotiation}{Negot.}
\hi@abbrev{Negotiations}{Negots.}
\hi@abbrev{New Series}{n\abb@dot s\abb@dot }
\hi@abbrev{Newsletter}{Newsl.}
\hi@abbrev{Newsletters}{Newsls.}
\hi@abbrev{Office}{Off.}
\hi@abbrev{Offices}{Offs.}
\hi@abbrev{Order}{Ord.}
\hi@abbrev{Orders}{Ords.}
\hi@abbrev{Organization}{Org.}
\hi@abbrev{Organizations}{Orgs.}
\hi@abbrev{Pacific}{Pac.}
\hi@abbrev{Pacifics}{Pacs.}
\hi@abbrev{Patent}{Pat.}
\hi@abbrev{Patents}{Pats.}
\hi@abbrev{Personal}{Pers.}
\hi@abbrev{Personals}{Perss.}
\hi@abbrev{Perpsectives}{Persp.}
\hi@abbrev{Philosophical}{Phil.}
\hi@abbrev{Philosophicals}{Phils.}
\hi@abbrev{Philosophy}{Phil.}
\hi@abbrev{Philosophies}{Phils.}
\hi@abbrev{Planning}{Plan.}
\hi@abbrev{Plannings}{Plans.}
\hi@abbrev{Policy}{Pol'y}
\hi@abbrev{Policies}{Pol'ys}
\hi@abbrev{Political}{Pol.}
\hi@abbrev{Politicals}{Pols.}
\hi@abbrev{Politics}{Pol.}
\hi@abbrev{Politicses}{Pols.}
\hi@abbrev{Practical}{Prac.}
\hi@abbrev{Practicals}{Pracs.}
\hi@abbrev{Practice}{Prac.}
\hi@abbrev{Practices}{Pracs.}
\hi@abbrev{Practitioner(s)}{Prac.}
\hi@abbrev{Practitioner(s)s}{Pracs.}
\hi@abbrev{Private}{Priv.}
\hi@abbrev{Privates}{Privs.}
\hi@abbrev{Probate}{Prob.}
\hi@abbrev{Probates}{Probs.}
\hi@abbrev{Probation}{Prob.}
\hi@abbrev{Probations}{Probs.}
\hi@abbrev{Problems}{Probs.}
\hi@abbrev{Problemses}{Probss.}
\hi@abbrev{Proceedings}{Proc.}
\hi@abbrev{Proceedingses}{Procs.}
\hi@abbrev{Procedure}{Proc.}
\hi@abbrev{Procedures}{Procs.}
\hi@abbrev{Products Liability}{Prod. Liab.}
\hi@abbrev{Products Liabilities}{Prod. Liabs.}
\hi@abbrev{Professional}{Prof.}
\hi@abbrev{Professionals}{Profs.}
\hi@abbrev{Property}{Prop.}
\hi@abbrev{Properties}{Props.}
\hi@abbrev{Psychological}{Psychol.}
\hi@abbrev{Psychologicals}{Psychols.}
\hi@abbrev{Psychology}{Psychol.}
\hi@abbrev{Psychologies}{Psychols.}
\hi@abbrev{Public}{Pub.}
\hi@abbrev{Publics}{Pubs.}
\hi@abbrev{Publishing}{Pub.}
\hi@abbrev{Publishings}{Pubs.}
\hi@abbrev{Quarterly}{Q\abb@dot }
\hi@abbrev{Quarterlies}{Qs.}
\hi@abbrev{Record}{Rec.}
\hi@abbrev{Records}{Recs.}
\hi@abbrev{Referees}{Ref.}
\hi@abbrev{Register}{Reg.}
\hi@abbrev{Registers}{Regs.}
\hi@abbrev{Regulation}{Reg.}
\hi@abbrev{Regulations}{Regs.}
\hi@abbrev{Regulatory}{Reg.}
\hi@abbrev{Regulatories}{Regs.}
\hi@abbrev{Relations}{Rel.}
\hi@abbrev{Relationses}{Rels.}
\hi@abbrev{Reports}{Rep.}
\hi@abbrev{Reportses}{Reps.}
\hi@abbrev{Reporter}{Rep.}
\hi@abbrev{Reporters}{Reps.}
\hi@abbrev{Reproduction}{Reprod.}
\hi@abbrev{Reproductions}{Reprods.}
\hi@abbrev{Reproductive}{Reprod.}
\hi@abbrev{Reproductives}{Reprods.}
\hi@abbrev{Research}{Res.}
\hi@abbrev{Researches}{Ress.}
\hi@abbrev{Reserve}{Res.}
\hi@abbrev{Reserves}{Ress.}
\hi@abbrev{Resolution}{Resol.}
\hi@abbrev{Resolutions}{Resols.}
\hi@abbrev{Responsibility}{Resp.}
\hi@abbrev{Responsibilities}{Resps.}
\hi@abbrev{Review}{Rev.}
\hi@abbrev{Reviews}{Revs.}
\hi@abbrev{Revista}{Rev.}
\hi@abbrev{Revistas}{Revs.}
\hi@abbrev{Rights}{Rts.}
\hi@abbrev{Rightses}{Rtss.}
\hi@abbrev{School}{Sch.}
\hi@abbrev{Schools}{Schs.}
\hi@abbrev{Science}{Sci.}
\hi@abbrev{Sciences}{Sci.}
\hi@abbrev{Scientific}{Sci.}
\hi@abbrev{Scientifics}{Scis.}
\hi@abbrev{Scottish}{Scot.}
\hi@abbrev{Scottishes}{Scots.}
\hi@abbrev{Section}{Sec.}
\hi@abbrev{Sections}{Secs.}
\hi@abbrev{Securities}{Sec.}
\hi@abbrev{Sentencing}{Sent'g}
\hi@abbrev{Sentencings}{Sent'gs}
\hi@abbrev{Service}{Serv.}
\hi@abbrev{Services}{Servs.}
\hi@abbrev{Social}{Soc.}
\hi@abbrev{Socials}{Socs.}
\hi@abbrev{Society}{Soc'y}
\hi@abbrev{Societies}{Soc'ys}
\hi@abbrev{Sociological}{Soc.}
\hi@abbrev{Sociologicals}{Socs.}
\hi@abbrev{Sociology}{Soc.}
\hi@abbrev{Sociologies}{Socs.}
\hi@abbrev{Solicitors}{Solic.}
\hi@abbrev{Solicitorses}{Solics.}
\hi@abbrev{Solicitors'}{Solic.}
\hi@abbrev{Solicitor's}{Solic.}
\hi@abbrev{State}{St.}
\hi@abbrev{States}{Sts.}
\hi@abbrev{Statistics}{Stat.}
\hi@abbrev{Statisticses}{Stats.}
\hi@abbrev{Statistical}{Stat.}
\hi@abbrev{Statisticals}{Stats.}
\hi@abbrev{Studies}{Stud.}
\hi@abbrev{Supreme Court}{Sup. Ct.}
\hi@abbrev{Supreme Courts}{Sup. Cts.}
\hi@abbrev{Survey}{Surv.}
\hi@abbrev{Surveys}{Survs.}
\hi@abbrev{Symposium}{Symp.}
\hi@abbrev{Symposia}{Symps.}
\hi@abbrev{Symposiums}{Symps.}
\hi@abbrev{System}{Sys.}
\hi@abbrev{Systems}{Syss.}
\hi@abbrev{Taxation}{Tax'n}
\hi@abbrev{Taxations}{Tax'ns}
\hi@abbrev{Teacher}{Tchr.}
\hi@abbrev{Teachers}{Tchrs.}
\hi@abbrev{Technique}{Tech.}
\hi@abbrev{Techniques}{Techs.}
\hi@abbrev{Technology}{Tech.}
\hi@abbrev{Technologies}{Techs.}
\hi@abbrev{Telecommunications}{Telecomm.}
\hi@abbrev{Telecommunicationses}{Telecomms.}
\hi@abbrev{Transnational}{Transnat'l}
\hi@abbrev{Transnationals}{Transnat'ls}
\hi@abbrev{Transportation}{Transp.}
\hi@abbrev{Transportations}{Transps.}
\hi@abbrev{Tribune}{Trib.}
\hi@abbrev{Tribunes}{Tribs.}
\hi@abbrev{Trustee}{Tr.}
\hi@abbrev{Trustees}{Trs.}
\hi@abbrev{Trusts}{Tr.}
\hi@abbrev{Trustses}{Trs.}
\hi@abbrev{Uniform Commercial Code}{UCC}
\hi@abbrev{Uniform Commercial Codes}{UCCs}
\hi@abbrev{Urban}{Urb.}
\hi@abbrev{Urbans}{Urbs.}
\hi@abbrev{Utilities}{Util.}
\hi@abbrev{Utility}{Util.}
\hi@abbrev{Week}{Wk.}
\hi@abbrev{Weeks}{Wks.}
\hi@abbrev{Weekly}{Wkly.}
\hi@abbrev{Weeklies}{Wklys.}
\hi@abbrev{Yearbook}{Y\abb@dot B\abb@dot }
\hi@abbrev{Yearbooks}{Y\abb@dot Bs.}
\hi@abbrev{Year Book}{Y\abb@dot B\abb@dot }
\hi@abbrev{Year Books}{Y\abb@dot Bs.}
