%
% Abbreviations for names, from Indigo Book Table 11
%
\hi@abbrev{Academ}{Acad.}
\hi@abbrev{Academs}{Acads.}
\hi@abbrev{Academic}{Acad.}
\hi@abbrev{Academics}{Acads.}
\hi@abbrev{Academy}{Acad.}
\hi@abbrev{Academies}{Acads.}
\hi@abbrev{Administrat}{Admin.}
\hi@abbrev{Administrats}{Admins.}
\hi@abbrev{Administrative}{Admin.}
\hi@abbrev{Administratives}{Admins.}
\hi@abbrev{Administration}{Admin.}
\hi@abbrev{Administrations}{Admins.}
\hi@abbrev{Administrats}{Adm's}
\hi@abbrev{Administrator}{Adm'r}
\hi@abbrev{Administrators}{Adm'rs}
\hi@abbrev{Administratrix}{Adm'x}
\hi@abbrev{Administratrixes}{Adm'xs}
\hi@abbrev{Administratrices}{Adm'xs}
\hi@abbrev{Advertising}{Advert.}
\hi@abbrev{Advertisings}{Adverts.}
\hi@abbrev{Agricultur}{Agric.}
\hi@abbrev{Agriculturs}{Agrics.}
\hi@abbrev{Agriculture}{Agric.}
\hi@abbrev{Agricultures}{Agrics.}
\hi@abbrev{Agricultural}{Agric.}
\hi@abbrev{Agriculturals}{Agrics.}
\hi@abbrev{Alliance}{All.}
\hi@abbrev{Alliances}{Alls.}
\hi@abbrev{Alternative}{Alt.}
\hi@abbrev{Alternatives}{Alts.}
\hi@abbrev{America}{Am.}
\hi@abbrev{Americas}{Ams.}
\hi@abbrev{American}{Am.}
\hi@abbrev{Americans}{Ams.}
\hi@abbrev{and}{&}
\hi@abbrev{ands}{&s}
\hi@abbrev{Associate}{Assoc.}
\hi@abbrev{Associates}{Assocs.}
\hi@abbrev{Association}{Ass'n}
\hi@abbrev{Associations}{Ass'ns}
\hi@abbrev{Atlantic}{Atl.}
\hi@abbrev{Atlantics}{Atls.}
\hi@abbrev{Authority}{Auth.}
\hi@abbrev{Authorities}{Auths.}
\hi@abbrev{Automo}{Auto.}
\hi@abbrev{Automos}{Autos.}
\hi@abbrev{Automobile}{Auto.}
\hi@abbrev{Automobiles}{Autos.}
\hi@abbrev{Automotive}{Auto.}
\hi@abbrev{Automotives}{Autos.}
\hi@abbrev{Avenue}{Ave.}
\hi@abbrev{Avenues}{Aves.}
\hi@abbrev{Bankruptcy}{Bankr.}
\hi@abbrev{Bankruptcies}{Bankrs.}
\hi@abbrev{Board}{Bd.}
\hi@abbrev{Boards}{Bds.}
\hi@abbrev{Broadcast}{Broad.}
\hi@abbrev{Broadcasts}{Broads.}
\hi@abbrev{Broadcaster}{Broad.}
\hi@abbrev{Broadcasters}{Broads.}
\hi@abbrev{Broadcasting}{Broad.}
\hi@abbrev{Broadcastings}{Broads.}
\hi@abbrev{Brotherhood}{Bhd.}
\hi@abbrev{Brotherhoods}{Bhds.}
\hi@abbrev{Brothers}{Bros.}
\hi@abbrev{Brotherses}{Bross.}
\hi@abbrev{Building}{Bldg.}
\hi@abbrev{Buildings}{Bldgs.}
\hi@abbrev{Business}{Bus.}
\hi@abbrev{Businesses}{Buss.}
\hi@abbrev{Casualty}{Cas.}
\hi@abbrev{Casualties}{Cass.}
\hi@abbrev{Cent}{Ctr.}
\hi@abbrev{Cents}{Ctrs.}
\hi@abbrev{Center}{Ctr.}
\hi@abbrev{Centers}{Ctrs.}
\hi@abbrev{Centre}{Ctr.}
\hi@abbrev{Centres}{Ctrs.}
\hi@abbrev{Central}{Cent.}
\hi@abbrev{Centrals}{Cents.}
\hi@abbrev{Chemical}{Chem.}
\hi@abbrev{Chemicals}{Chems.}
\hi@abbrev{Coalition}{Coal.}
\hi@abbrev{Coalitions}{Coals.}
\hi@abbrev{College}{Coll.}
\hi@abbrev{Colleges}{Colls.}
\hi@abbrev{Commission}{Comm'n}
\hi@abbrev{Commissions}{Comm'ns}
\hi@abbrev{Commissioner}{Comm'r}
\hi@abbrev{Commissioners}{Comm'rs}
\hi@abbrev{Committee}{Comm.}
\hi@abbrev{Committees}{Comms.}
\hi@abbrev{Communication}{Commc'n}
\hi@abbrev{Communications}{Commc'ns}
\hi@abbrev{Community}{Cmty.}
\hi@abbrev{Communities}{Cmtys.}
\hi@abbrev{Company}{Co.}
\hi@abbrev{Companies}{Cos.}
\hi@abbrev{Compensation}{Comp.}
\hi@abbrev{Compensations}{Comps.}
\hi@abbrev{Computer}{Comput.}
\hi@abbrev{Computers}{Computs.}
\hi@abbrev{Condominium}{Condo.}
\hi@abbrev{Condominiums}{Condos.}
\hi@abbrev{Congress}{Cong.}
\hi@abbrev{Congresses}{Congs.}
\hi@abbrev{Congressional}{Cong.}
\hi@abbrev{Congressionals}{Congs.}
\hi@abbrev{Consolidated}{Consol.}
\hi@abbrev{Consolidateds}{Consols.}
\hi@abbrev{Construction}{Constr.}
\hi@abbrev{Constructions}{Constrs.}
\hi@abbrev{Continental}{Cont'l}
\hi@abbrev{Continentals}{Cont'ls}
\hi@abbrev{Cooperative}{Coop.}
\hi@abbrev{Cooperatives}{Coops.}
\hi@abbrev{Corporat}{Corp.}
\hi@abbrev{Corporats}{Corps.}
\hi@abbrev{Corporate}{Corp.}
\hi@abbrev{Corporates}{Corps.}
\hi@abbrev{Corporation}{Corp.}
\hi@abbrev{Corporations}{Corps.}
\hi@abbrev{Correction}{Corr.}
\hi@abbrev{Corrections}{Corr.}
\hi@abbrev{Correctional}{Corr.}
\hi@abbrev{Correctionals}{Corrs.}
\hi@abbrev{County}{Cty.}
\hi@abbrev{Counties}{Ctys.}
\hi@abbrev{Defen}{Def.}
\hi@abbrev{Defens}{Defs.}
\hi@abbrev{Defender}{Def.}
\hi@abbrev{Defenders}{Defs.}
\hi@abbrev{Defense}{Def.}
\hi@abbrev{Defenses}{Defs.}
\hi@abbrev{Department}{Dep't}
\hi@abbrev{Departments}{Dep'ts}
\hi@abbrev{Detention}{Det.}
\hi@abbrev{Detentions}{Dets.}
\hi@abbrev{Development}{Dev.}
\hi@abbrev{Developments}{Devs.}
\hi@abbrev{Digital}{Dig.}
\hi@abbrev{Digitals}{Digs.}
\hi@abbrev{Director}{Dir.}
\hi@abbrev{Directors}{Dirs.}
\hi@abbrev{Discount}{Disc.}
\hi@abbrev{Discounts}{Discs.}
\hi@abbrev{Distribut}{Distrib.}
\hi@abbrev{Distributs}{Distribs.}
\hi@abbrev{Distributor}{Distrib.}
\hi@abbrev{Distributors}{Distribs.}
\hi@abbrev{Distributing}{Distrib.}
\hi@abbrev{Distributings}{Distribs.}
\hi@abbrev{District}{Dist.}
\hi@abbrev{Districts}{Dists.}
\hi@abbrev{Division}{Div.}
\hi@abbrev{Divisions}{Divs.}
\hi@abbrev{East}{E.}
\hi@abbrev{Easts}{Es.}
\hi@abbrev{Eastern}{E.}
\hi@abbrev{Easterns}{Es.}
\hi@abbrev{Econom}{Econ.}
\hi@abbrev{Economs}{Econs.}
\hi@abbrev{Economic}{Econ.}
\hi@abbrev{Economical}{Econ.}
\hi@abbrev{Economicals}{Econs.}
\hi@abbrev{Economics}{Econ.}
\hi@abbrev{Economy}{Econ.}
\hi@abbrev{Economies}{Econs.}
\hi@abbrev{Education}{Educ.}
\hi@abbrev{Educations}{Educs.}
\hi@abbrev{Educational}{Educ.}
\hi@abbrev{Educationals}{Educs.}
\hi@abbrev{Electr}{Elec.}
\hi@abbrev{Electrs}{Elecs.}
\hi@abbrev{Electric}{Elec.}
\hi@abbrev{Electrics}{Elecs.}
\hi@abbrev{Electrical}{Elec.}
\hi@abbrev{Electricals}{Elecs.}
\hi@abbrev{Electricity}{Elec.}
\hi@abbrev{Electricities}{Elecs.}
\hi@abbrev{Electronic}{Elec.}
\hi@abbrev{Electronics}{Elecs.}
\hi@abbrev{Employee}{Emp.}
\hi@abbrev{Employees}{Emps.}
\hi@abbrev{Employs}{Emp's}
\hi@abbrev{Employer}{Emp'r}
\hi@abbrev{Employers}{Emp'rs}
\hi@abbrev{Employment}{Emp't}
\hi@abbrev{Employments}{Emp'ts}
\hi@abbrev{Enforcement}{Enf't}
\hi@abbrev{Enforcements}{Enf'ts}
\hi@abbrev{Engineer}{Eng'r}
\hi@abbrev{Engineers}{Eng'rs}
\hi@abbrev{Engineering}{Eng'g}
\hi@abbrev{Engineerings}{Eng'gs}
\hi@abbrev{Enterprise}{Enter.}
\hi@abbrev{Enterprises}{Enters.}
\hi@abbrev{Entertainment}{Entm't}
\hi@abbrev{Entertainments}{Entm'ts}
\hi@abbrev{Environment}{Env't}
\hi@abbrev{Environments}{Env'ts}
\hi@abbrev{Environmental}{Envtl.}
\hi@abbrev{Environmentals}{Envtls.}
\hi@abbrev{Equality}{Equal.}
\hi@abbrev{Equalities}{Equals.}
\hi@abbrev{Equipment}{Equip.}
\hi@abbrev{Equipments}{Equips.}
\hi@abbrev{Examiner}{Exam'r}
\hi@abbrev{Examiners}{Exam'rs}
\hi@abbrev{Exchange}{Exch.}
\hi@abbrev{Exchanges}{Exchs.}
\hi@abbrev{Executive}{Exec.}
\hi@abbrev{Executives}{Execs.}
\hi@abbrev{Executs}{Ex's}
\hi@abbrev{Executor}{Ex'r}
\hi@abbrev{Executors}{Ex'rs}
\hi@abbrev{Executrix}{Ex'x}
\hi@abbrev{Executrixes}{Ex'xs}
\hi@abbrev{Executrices}{Ex'xs}
\hi@abbrev{Explorat}{Expl.}
\hi@abbrev{Explorats}{Expls.}
\hi@abbrev{Exploration}{Expl.}
\hi@abbrev{Explorations}{Expls.}
\hi@abbrev{Exploratory}{Expl.}
\hi@abbrev{Exploratories}{Expls.}
\hi@abbrev{Export}{Exp.}
\hi@abbrev{Exports}{Exps.}
\hi@abbrev{Exporter}{Exp.}
\hi@abbrev{Exporters}{Exps.}
\hi@abbrev{Exportation}{Exp.}
\hi@abbrev{Exportations}{Exps.}
\hi@abbrev{Federal}{Fed.}
\hi@abbrev{Federals}{Feds.}
\hi@abbrev{Federation}{Fed'n}
\hi@abbrev{Federations}{Fed'ns}
\hi@abbrev{Fidelity}{Fid.}
\hi@abbrev{Fidelities}{Fids.}
\hi@abbrev{Financ}{Fin.}
\hi@abbrev{Financs}{Fins.}
\hi@abbrev{Finance}{Fin.}
\hi@abbrev{Finances}{Fins.}
\hi@abbrev{Financial}{Fin.}
\hi@abbrev{Financials}{Fins.}
\hi@abbrev{Financing}{Fin.}
\hi@abbrev{Financings}{Fins.}
\hi@abbrev{Foundation}{Found.}
\hi@abbrev{Foundations}{Founds.}
\hi@abbrev{General}{Gen.}
\hi@abbrev{Generals}{Gens.}
\hi@abbrev{Global}{Glob.}
\hi@abbrev{Globals}{Globs.}
\hi@abbrev{Government}{Gov't}
\hi@abbrev{Governments}{Gov'ts}
\hi@abbrev{Group}{Grp.}
\hi@abbrev{Groups}{Grps.}
\hi@abbrev{Guaranty}{Guar.}
\hi@abbrev{Guaranties}{Guars.}
\hi@abbrev{Hospital}{Hosp.}
\hi@abbrev{Hospitals}{Hosps.}
\hi@abbrev{Hospitality}{Hosp.}
\hi@abbrev{Hospitalities}{Hosps.}
\hi@abbrev{Housing}{Hous.}
\hi@abbrev{Housings}{Houss.}
\hi@abbrev{Import}{Imp.}
\hi@abbrev{Imports}{Imps.}
\hi@abbrev{Importer}{Imp.}
\hi@abbrev{Importers}{Imps.}
\hi@abbrev{Importation}{Imp.}
\hi@abbrev{Importations}{Imps.}
\hi@abbrev{Incorporated}{Inc.}
\hi@abbrev{Incorporateds}{Incs.}
\hi@abbrev{Indemnity}{Indem.}
\hi@abbrev{Indemnities}{Indems.}
\hi@abbrev{Independen}{Indep.}
\hi@abbrev{Independens}{Indeps.}
\hi@abbrev{Independence}{Indep.}
\hi@abbrev{Independences}{Indeps.}
\hi@abbrev{Independent}{Indep.}
\hi@abbrev{Independents}{Indeps.}
\hi@abbrev{Industr}{Indus.}
\hi@abbrev{Industrs}{Induss.}
\hi@abbrev{Industry}{Indus.}
\hi@abbrev{Industries}{Indus.}
\hi@abbrev{Industrial}{Indus.}
\hi@abbrev{Industrials}{Induss.}
\hi@abbrev{Information}{Info.}
\hi@abbrev{Informations}{Infos.}
\hi@abbrev{Institut}{Inst.}
\hi@abbrev{Instituts}{Insts.}
\hi@abbrev{Institute}{Inst.}
\hi@abbrev{Institutes}{Insts.}
\hi@abbrev{Institution}{Inst.}
\hi@abbrev{Institutions}{Insts.}
\hi@abbrev{Insurance}{Ins.}
\hi@abbrev{Insurances}{Inss.}
\hi@abbrev{International}{Int'l}
\hi@abbrev{Internationals}{Int'ls}
\hi@abbrev{Investment}{Inv.}
\hi@abbrev{Investments}{Invs.}
\hi@abbrev{Investor}{Inv'r}
\hi@abbrev{Investors}{Inv'rs}
\hi@abbrev{Laboratory}{Lab.}
\hi@abbrev{Laboratories}{Labs.}
\hi@abbrev{Liability}{Liab.}
\hi@abbrev{Liabilities}{Liabs.}
\hi@abbrev{Limited}{Ltd.}
\hi@abbrev{Limiteds}{Ltds.}
\hi@abbrev{Litigation}{Litig.}
\hi@abbrev{Litigations}{Litigs.}
\hi@abbrev{Machine}{Mach.}
\hi@abbrev{Machines}{Machs.}
\hi@abbrev{Machinery}{Mach.}
\hi@abbrev{Machineries}{Machs.}
\hi@abbrev{Maintenance}{Maint.}
\hi@abbrev{Maintenances}{Maints.}
\hi@abbrev{Management}{Mgmt.}
\hi@abbrev{Managements}{Mgmts.}
\hi@abbrev{Manufacturer}{Mfr.}
\hi@abbrev{Manufacturers}{Mfrs.}
\hi@abbrev{Manufacturing}{Mfg.}
\hi@abbrev{Manufacturings}{Mfgs.}
\hi@abbrev{Maritime}{Mar.}
\hi@abbrev{Maritimes}{Mars.}
\hi@abbrev{Market}{Mkt.}
\hi@abbrev{Markets}{Mkts.}
\hi@abbrev{Marketing}{Mktg.}
\hi@abbrev{Marketings}{Mktgs.}
\hi@abbrev{Mechanic}{Mech.}
\hi@abbrev{Mechanics}{Mechs.}
\hi@abbrev{Mechanical}{Mech.}
\hi@abbrev{Mechanicals}{Mechs.}
\hi@abbrev{Medic}{Med.}
\hi@abbrev{Medics}{Meds.}
\hi@abbrev{Medical}{Med.}
\hi@abbrev{Medicals}{Meds.}
\hi@abbrev{Medicine}{Med.}
\hi@abbrev{Medicines}{Meds.}
\hi@abbrev{Memorial}{Mem'l}
\hi@abbrev{Memorials}{Mem'ls}
\hi@abbrev{Merchan}{Merch.}
\hi@abbrev{Merchans}{Merchs.}
\hi@abbrev{Merchant}{Merch.}
\hi@abbrev{Merchants}{Merchs.}
\hi@abbrev{Merchandise}{Merch.}
\hi@abbrev{Merchandises}{Merchs.}
\hi@abbrev{Merchandising}{Merch.}
\hi@abbrev{Merchandisings}{Merchs.}
\hi@abbrev{Metropolitan}{Metro.}
\hi@abbrev{Metropolitans}{Metros.}
\hi@abbrev{Mortgage}{Mortg.}
\hi@abbrev{Mortgages}{Mortgs.}
\hi@abbrev{Municipal}{Mun.}
\hi@abbrev{Municipals}{Muns.}
\hi@abbrev{Mutual}{Mut.}
\hi@abbrev{Mutuals}{Muts.}
\hi@abbrev{National}{Nat'l}
\hi@abbrev{Nationals}{Nat'ls}
\hi@abbrev{Natural}{Nat.}
\hi@abbrev{Naturals}{Nats.}
\hi@abbrev{North}{N.}
\hi@abbrev{Norths}{Ns.}
\hi@abbrev{Northern}{N.}
\hi@abbrev{Northerns}{Ns.}
\hi@abbrev{Northeast}{Ne.}
\hi@abbrev{Northeasts}{Nes.}
\hi@abbrev{Northeastern}{Ne.}
\hi@abbrev{Northeasterns}{Nes.}
\hi@abbrev{Northwest}{Nw.}
\hi@abbrev{Northwests}{Nws.}
\hi@abbrev{Northwestern}{Nw.}
\hi@abbrev{Northwesterns}{Nws.}
\hi@abbrev{Number}{No.}
\hi@abbrev{Numbers}{Nos.}
\hi@abbrev{Opinion}{Op.}
\hi@abbrev{Opinions}{Ops.}
\hi@abbrev{Organiz}{Org.}
\hi@abbrev{Organizes}{Orgs.}
\hi@abbrev{Organization}{Org.}
\hi@abbrev{Organizations}{Orgs.}
\hi@abbrev{Organizing}{Org.}
\hi@abbrev{Organizings}{Orgs.}
\hi@abbrev{Pacific}{Pac.}
\hi@abbrev{Pacifics}{Pacs.}
\hi@abbrev{Parish}{Par.}
\hi@abbrev{Parishes}{Pars.}
\hi@abbrev{Partnership}{P'ship}
\hi@abbrev{Partnerships}{P'ships}
\hi@abbrev{Person}{Pers.}
\hi@abbrev{Persons}{Perss.}
\hi@abbrev{Personal}{Pers.}
\hi@abbrev{Personals}{Perss.}
\hi@abbrev{Personnel}{Pers.}
\hi@abbrev{Personnels}{Perss.}
\hi@abbrev{Pharmaceutic}{Pharm.}
\hi@abbrev{Pharmaceutics}{Pharm.}
\hi@abbrev{Pharmaceutical}{Pharm.}
\hi@abbrev{Pharmaceuticals}{Pharm.}
\hi@abbrev{Preserv}{Pres.}
\hi@abbrev{Preservs}{Press.}
\hi@abbrev{Preserve}{Pres.}
\hi@abbrev{Preserves}{Press.}
\hi@abbrev{Preservation}{Pres.}
\hi@abbrev{Preservations}{Press.}
\hi@abbrev{Probat}{Prob.}
\hi@abbrev{Probats}{Probs.}
\hi@abbrev{Probate}{Prob.}
\hi@abbrev{Probates}{Probs.}
\hi@abbrev{Probation}{Prob.}
\hi@abbrev{Probations}{Probs.}
\hi@abbrev{Product}{Prod.}
\hi@abbrev{Products}{Prods.}
\hi@abbrev{Production}{Prod.}
\hi@abbrev{Productions}{Prods.}
\hi@abbrev{Professional}{Prof'l}
\hi@abbrev{Professionals}{Prof'ls}
\hi@abbrev{Property}{Prop.}
\hi@abbrev{Properties}{Props.}
\hi@abbrev{Protection}{Prot.}
\hi@abbrev{Protections}{Prots.}
\hi@abbrev{Public}{Pub.}
\hi@abbrev{Publics}{Pubs.}
\hi@abbrev{Publication}{Publ'n}
\hi@abbrev{Publications}{Publ'ns}
\hi@abbrev{Publishing}{Publ'g}
\hi@abbrev{Publishings}{Publ'gs}
\hi@abbrev{Railroad}{R.R.}
\hi@abbrev{Railroads}{R.Rs.}
\hi@abbrev{Railway}{Ry.}
\hi@abbrev{Railways}{Rys.}
\hi@abbrev{Refining}{Ref.}
\hi@abbrev{Refinings}{Refs.}
\hi@abbrev{Regional}{Reg'l}
\hi@abbrev{Regionals}{Reg'ls}
\hi@abbrev{Rehabilitat}{Rehab.}
\hi@abbrev{Rehabilitats}{Rehabs.}
\hi@abbrev{Rehabilitation}{Rehab.}
\hi@abbrev{Rehabilitations}{Rehabs.}
\hi@abbrev{Rehabilitative}{Rehab.}
\hi@abbrev{Rehabilitatives}{Rehabs.}
\hi@abbrev{Reproduct}{Reprod.}
\hi@abbrev{Reproducts}{Reprods.}
\hi@abbrev{Reproduction}{Reprod.}
\hi@abbrev{Reproductions}{Reprods.}
\hi@abbrev{Reproductive}{Reprod.}
\hi@abbrev{Reproductives}{Reprods.}
\hi@abbrev{Resource}{Res.}
\hi@abbrev{Resources}{Res.}
\hi@abbrev{Restaurant}{Rest.}
\hi@abbrev{Restaurants}{Rests.}
\hi@abbrev{Retirement}{Ret.}
\hi@abbrev{Retirements}{Rets.}
\hi@abbrev{Road}{Rd.}
\hi@abbrev{Roads}{Rds.}
\hi@abbrev{Savings}{Sav.}
\hi@abbrev{Savingses}{Savs.}
\hi@abbrev{School}{Sch.}
\hi@abbrev{Schools}{Sch.}
\hi@abbrev{Scien}{Sci.}
\hi@abbrev{Sciens}{Scis.}
\hi@abbrev{Science}{Sci.}
\hi@abbrev{Sciences}{Scis.}
\hi@abbrev{Scientific}{Sci.}
\hi@abbrev{Scientifics}{Scis.}
\hi@abbrev{Secretary}{Sec'y}
\hi@abbrev{Secretaries}{Sec'ys}
\hi@abbrev{Securit}{Sec.}
\hi@abbrev{Securits}{Secs.}
\hi@abbrev{Security}{Sec.}
\hi@abbrev{Securities}{Sec.}
\hi@abbrev{Service}{Serv.}
\hi@abbrev{Services}{Servs.}
\hi@abbrev{Shareholder}{S'holder}
\hi@abbrev{Shareholders}{S'holders}
\hi@abbrev{Social}{Soc.}
\hi@abbrev{Socials}{Socs.}
\hi@abbrev{Society}{Soc'y}
\hi@abbrev{Societies}{Soc'ys}
\hi@abbrev{Solution}{Sol.}
\hi@abbrev{Solutions}{Sols.}
\hi@abbrev{South}{S.}
\hi@abbrev{Souths}{Ss.}
\hi@abbrev{Southern}{S.}
\hi@abbrev{Southerns}{Ss.}
\hi@abbrev{Southeast}{Se.}
\hi@abbrev{Southeasts}{Ses.}
\hi@abbrev{Southeastern}{Se.}
\hi@abbrev{Southeasterns}{Ses.}
\hi@abbrev{Southwest}{Sw.}
\hi@abbrev{Southwests}{Sws.}
\hi@abbrev{Southwestern}{Sw.}
\hi@abbrev{Southwesterns}{Sws.}
\hi@abbrev{Steamship}{S.S.}
\hi@abbrev{Steamships}{S.S.}
\hi@abbrev{Street}{St.}
\hi@abbrev{Streets}{Sts.}
\hi@abbrev{Subcommittee}{Subcomm.}
\hi@abbrev{Subcommittees}{Subcomms.}
\hi@abbrev{Surety}{Sur.}
\hi@abbrev{Sureties}{Surs.}
\hi@abbrev{System}{Sys.}
\hi@abbrev{Systems}{Sys.}
\hi@abbrev{Techn}{Tech.}
\hi@abbrev{Techns}{Techs.}
\hi@abbrev{Technical}{Tech.}
\hi@abbrev{Technicals}{Techs.}
\hi@abbrev{Technological}{Tech.}
\hi@abbrev{Technologicals}{Techs.}
\hi@abbrev{Technology}{Tech.}
\hi@abbrev{Technologies}{Techs.}
\hi@abbrev{Telecommunication}{Telecomm.}
\hi@abbrev{Telecommunications}{Telecomms.}
\hi@abbrev{Tele}{Tel.}
\hi@abbrev{Teles}{Tels.}
\hi@abbrev{Telephone}{Tel.}
\hi@abbrev{Telephones}{Tels.}
\hi@abbrev{Telegraph}{Tel.}
\hi@abbrev{Telegraphs}{Tels.}
\hi@abbrev{Temporary}{Temp.}
\hi@abbrev{Temporaries}{Temps.}
\hi@abbrev{Township}{Twp.}
\hi@abbrev{Townships}{Twps.}
\hi@abbrev{Transcontinental}{Transcon.}
\hi@abbrev{Transcontinentals}{Transcons.}
\hi@abbrev{Transport}{Transp.}
\hi@abbrev{Transports}{Transps.}
\hi@abbrev{Transportation}{Transp.}
\hi@abbrev{Transportations}{Transps.}
\hi@abbrev{Trust}{Tr.}
\hi@abbrev{Trusts}{Trs.}
\hi@abbrev{Trustee}{Tr.}
\hi@abbrev{Trustees}{Trs.}
\hi@abbrev{Turnpike}{Tpk.}
\hi@abbrev{Turnpikes}{Tpks.}
\hi@abbrev{Uniform}{Unif.}
\hi@abbrev{Uniforms}{Unifs.}
\hi@abbrev{University}{Univ.}
\hi@abbrev{Universities}{Univs.}
\hi@abbrev{Utility}{Util.}
\hi@abbrev{Utilities}{Utils.}
\hi@abbrev{Village}{Vill.}
\hi@abbrev{Villages}{Vills.}
\hi@abbrev{West}{W.}
\hi@abbrev{Wests}{Ws.}
\hi@abbrev{Western}{W.}
\hi@abbrev{Westerns}{Ws.}
